Synthesis of production rules for glycans

### 2020-10-16 papers/sugar-synth/experiments.tex
citation added

{\em Benchmark: }
We have applied our tool on three sets of real data (D1,D2,D3) and two sets of synthetic data (D4,D5). The molecules have been obtained from
respiratory mucins of a cystic fibrosis patient (D1),
horse chorionic gonadotropin (D2), SARS-CoV-2 spike protein T323/S325 (D3)~\cite{Jaiman2018,SarsCov2}.
The availability of clean data, where we are clear about the source and the collection
methodology used, limits our choices.

@@

{\em Results:} % We have applied \ourtool~on the data set. For each data set, we choose several
% parameter combinations to illustrate the relative performance of the tool.
% If we did not budget large enough parameters, then the tool fails to
% synthesize the rules.
% We present the rules learned after giving minimum resources.
% Our tool gave output that matched with the analysis of~\cite{Jaiman2018}
% in reasonable time.

@@

The synthesis for D4 takes 0.72 seconds. We can observe that by reducing the number of rules to learn, the tool fails to learn rules as it required minimum 7 rules.

% Currently, the tool does not have any objective function to optimize the synthesized rules.
% We are hoping to see more data sets such that we can develop a clearer picture
% for a reasonable objective function.
% The results suggest that the tool is potentially applicable to larger data sets.

>>>>

{\em Benchmark: }
We have applied our tool on three sets of real data (D1,D2,D3) and two sets of synthetic data (D4,D5). The molecules have been obtained from
respiratory mucins of a cystic fibrosis patient (D1),
horse chorionic gonadotropin (D2), SARS-CoV-2 spike protein T323/S325 (D3)~\cite{Jaiman2018,10.1093/glycob/cwaa042}.
The availability of clean data, where we are clear about the source and the collection
methodology used, limits our choices.

@@

{\em Results:} We have applied \ourtool~on the data set. For each data set, we choose several
parameter combinations to illustrate the relative performance of the tool.
If we did not budget large enough parameters, then the tool fails to
synthesize the rules.
We present the rules learned after giving minimum resources.
% Our tool gave output that matched with the analysis of~\cite{Jaiman2018}
% in reasonable time.

@@

The synthesis for D4 takes 0.72 seconds. We can observe that by reducing the number of rules to learn, the tool fails to learn rules as it required minimum 7 rules.
The results suggest that the tool is potentially applicable to larger data sets.

% Currently, the tool does not have any objective function to optimize the synthesized rules.
% We are hoping to see more data sets such that we can develop a clearer picture
% for a reasonable objective function.
